Appendix 2 - Fitting proposed path models using the C-statistic

### 2015-01-21 ch2_path_appendix2.Rmd
exploratory code revisions

---
title: "Appendix 2 - Fitting proposed path models"
author: "Whalen Dillon"
date: "December 17, 2014"
output: html_document
---
----
#### This appendix details steps 1-4 of calculating the *C*-statistic for fitting a path model in a generalized multilevel context (Shipley 2009).

>>>>

---
title: "Appendix 2 - Fitting proposed path models using the C-statistic"
author: "Whalen Dillon"
date: "December 17, 2014"
output: word_document
---
----
#### This appendix details steps 1-4 of calculating the *C*-statistic for fitting a path model in a generalized multilevel context (Shipley 2009).
